---
title: "Mock examen"
author: "Alanis S. Mulero Burgos"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output: 
  prettydoc::html_pretty:
   theme: architect
   highlight: github
---
## Parte 1: Base R

### Librerias
```{r message=F}
library(readxl)
library(dplyr)
```

### Data
```{r}
cereal <- readxl::read_excel("cereal.xlsx")
head(cereal)
```

### Pregunta 1
Extract rows 1 to 10 from the cereal data frame. 
```{r}
cereal[1:10, ]
```

### Pregunta 2
Create a new data frame called Kelloggs that only contains rows where company == “K”.
```{r}
Kelloggs <- subset(cereal, company == "K")
Kelloggs
```
 
### Pregunta 3
From the cereal data, extract the names of all cereals that have more than 10 grams of sugar.
```{r}
subset(cereal, sugars > 10)
```

### Pregunta 4
Find the mean calories of all cereals in the dataset.
```{r}
mean(cereal$calories)
```

### Pregunta 5
Count how many cereals have fiber greater than or equal to 2 grams
```{r}
length(cereal$fiber [cereal$fiber >= 2])
```

## Parte 2: dplyr

```{r}
library(dplyr)
library(readxl)
articles <- read.csv("EquationCitations.csv")
head(articles)
```

### Pregunta 1
On average, how many equations per article are published in each journal? (Hint: use group_by() and summarise())
```{r}
articles %>% 
  group_by(journal) %>% 
    summarize (average_eq = mean(equations))
```

### Pregunta 2
For each journal, calculate the average proportion of theoretical citations relative to total citations. (Hint: create a new column with mutate(theo_ratio = theocites / cites), then group_by() and summarise())
```{r}
articles %>% 
  mutate(theo_ratio = theocites/cites) %>% 
  group_by(journal) %>%
    summarize (mean_theo = mean(theo_ratio))
```

